Publishing Datasets about Building Designs \\Based on a Multilayer Building Ontology

### 2015-04-28 article-02-main.tex
Save draft for select types and defines types

% \begin{lstlisting}[caption={Simple data\-types as instances of \name{owl:Class}}, label=lst:ifcOWL-simple-types]
% expr:STRING a owl:Class;
%     rdfs:subClassOf [ a owl:Restriction;
%                       owl:onProperty rdf:value;
%                       owl:allValuesFrom xsd:double; ] .
% ifc:IfcTimeStamp a owl:Class;
%     rdfs:subClassOf [ a owl:Restriction;
%                       owl:onProperty rdf:value;
%                       owl:allValuesFrom xsd:dateTime; ]
% \end{lstlisting}

@@

@@

@@

\subsection{Entity Datatype Declarations}

\subsection{Enumeration Type Declarations}
\label{ifcOWL:enum-types}

>>>>

@@

\subsection{Select Datatype Declarations}
\label{subsec:ifcOWL-select-types}

A select data\-type represents an union of some defined, entity data\-types. For instance, data\-type \name{Ifc\-Trim\-ming\-Se\-lect} is an union of entity data\-type \name{Ifc\-Car\-te\-sian\-Point} and defined data\-type \name{Ifc\-Pa\-ra\-me\-ter\-Va\-lue}.

\begin{ontologyRule}[caption={Defined data\-types}]
A select data\-type is converted to an \name{owl:Class} that is equivalent to a union of \name{owl:Class} statements (see example on Listing \ref{lst:ifcOWL-select-types}).
\end{ontologyRule}

\begin{lstlisting}[caption={Select data\-types, label=lst:ifcOWL-select-types]
ifc:IfcTrimmingSelect owl:equivalentClass [
   rdf:type     owl:Class ;
   owl:unionOf  ( ifc:IfcCartesianPoint ifc:IfcparameterValue ) ] .
\end{lstlisting}

\TODO{Explain what if another OWL profile is used, and it doesn't support owl:unionOf --> use rdfs:subClassOf}

@@

A defined (declared, named) data\-type is usually specified as equivalent to a simple data\-type or another defined data\-type, with or without a constraint. For instance, type \name{Ifc\-Length\-Mea\-sure} is equal to \name{REAL}, and type \name{Ifc\-Po\-si\-ti\-ve\-Length\-Mea\-su\-re} is a set of positive \name{Ifc\-Length\-Mea\-sure} values.

In contrast to simple data\-types, defined data\-types can be used for declaration of select data\-types (see above), and most of defined data\-types have meaningful names. \TODO{When an entity property has select type which is a defined type...}
%Moreover, only a few of entity type properties in IFC are specified with simple data type.

\begin{ontologyRule}[caption={Defined data\-types}]
A defined data\-type is converted to an \name{owl:Class} with a single property \name{rdf:value} that has the underlying data\-type of the defined data\-type (see example on Listing \ref{lst:ifcOWL-defined-types}).
\end{ontologyRule}

\begin{lstlisting}[caption={Defined data\-types}, label=lst:ifcOWL-defined-types]
ifc:IfcAreaMeasure a owl:Class;
    rdfs:subClassOf [ a owl:Restriction;
                      owl:onProperty rdf:value;
                      owl:allValuesFrom xsd:double; ] .
\end{lstlisting}

Defined data\-types must be declared as wrapper classes because they must be instances of \name{owl:Class} can be used as a class-option of an union class (see \ref{subsec:ifcOWL-select-types}).

@@

\subsection{Entity Datatype Declarations}
\label{subsec:ifcOWL-entity-types}

Each entity data\-type represents a category of entity instances (entities). The main relationships between entities are inheritance and association (aggregation is considered as a special case of association).

similar to object model, single inheritance with properties.

\subsection{Enumeration Type Declarations}
\label{subsec:ifcOWL-enum-types}
